### 2021-07-12 write-up/submission.tex
Minor edits to README.md and final report

Initializing Bayesian machine learning models with empirical distributions from synthetic health records is a novel use of Synthea data that could provide insights in a variety of applications.  The Bayesian network model we have presented can be extended beyond the variables and demographics that we included.  It could be used to analyze detailed patient demographics, labs and results, medications, pre-existing conditions, and insurance information, all of which are already included in Synthea outputs.  In our current implementation, a researcher could use the model to look at likely causes for complex sets of symptoms, obtaining insights into multiple care trajectories in the face of uncertainty.  Exploration of this nature could account for various patient preferences and would contribute to patient-centered outcomes research, using the standard ``perfect" care trajectories written into the Synthea module to investigate complex care situations where perfect information isn't available.

>>>>

Initializing Bayesian machine learning models with empirical distributions from synthetic health records is a novel use of Synthea data that could provide insights in a variety of applications.  The Bayesian network model we have presented can be extended beyond the variables and demographics that we included.  It could be used to analyze more detailed patient demographics, labs and results, medications, pre-existing conditions, and insurance information, all of which are already included in Synthea outputs.  In our current implementation, a researcher could use the model to look at likely causes for complex sets of symptoms, obtaining insights into multiple diagnosis trajectories in the face of uncertainty.  Exploration of this nature could account for various patient preferences, contributing to patient-centered outcomes research.

This research could also provide valuable insights into the relative benefits of different inquiry paths.  Determining the actual value of any variable in the Bayesian network takes some amount of effort or resources.  Age and gender are easy to determine.  Determining symptoms and severities could require tools, time, facilities, or specialists.  The Bayesian models we present could be used to quantify the expected reduction in uncertainty that would come from conducting a certain inquiry to determine the value of a variable in the network, providing a measure of ``return on investment'' for a given test.  These methods can make use of the standard ``perfect" care trajectories written into the Synthea module to investigate complex care situations where perfect information isn't available.
